Self-assembly of colloid-cholesteric composites provides a route to switchable optical materials

### 2014-03-03 papers/2012-sandwich/response.txt

The term colloid is by the definition a dispersion of particles in a fluid.
Using the term also for the particles my lead to a confusion. In the
manuscript often also a more appropriate word
colloidal particle is used.

RESPONSE: We have standardised on "colloidal particle(s)" or simply
"particle(s)" where appropriate.

It would be important to add comments that would help experimentalist in
designing experiments with colloidal blue phases and perhaps stimulate
development of applications on the base of
these materials.

RESPONSE: The issue of experimental guidance is addressed in detail
in our reply to reviewer 2 below.

@@

In the discussion of the physical understanding of trapping of colloidal
particles in BP disclination networks it would be useful to refer to the
initial study by Ravnik et al. in Faraday
Discussions 2009 devoted to this topic.

RESPONSE: Citation for Ravnik et al Faraday Discuss. 2010 (sic) is added
[current reference 16].

250 K is more than the total mesophase stability range!

RESPONSE: A stability range for templated blue phases of -125 to
+125 degrees Celsius is reported by Castles et al. Nat. Mat. 2012.
We have made this connection more clear by rewriting the relevant
sentence: "However, recent advances in formulation have widened
this stability range enormously [11,12,13,14]. Most recently,
templated blue phases with a stability range of -125 to 125$^\circ$C
have been reported [Castles], paving the way to applications of BPs
in operational display devices."

@@

The statement "This is defined such that W > 0 gives preferential
perpendicular orientation of the director field at the particle surface." is
not consistent with the interaction form
described in the Supplement.

RESPONSE: We agree this statement is confusing. It has been replaced by
a clearer statement: "The anchoring strength is defined such that
W > 0 imparts a preferred orientation to the director field at the
particle surface. This orientation can be either normal to the
surface or in a plane tangential to the surface, a property related
to surface chemistry in experimental systems but which can be imposed
at will in simulations."

For potential readers it would be useful to specify the particle radius in
nanometers in the main text. How it compares to the nematic correlation
length? How the radius influences the
structures? How tiny the particles can still be that the method based on the
Landau-de Gennes free energy is justified.

RESPONSE: We have added in the main text (last paragraph introduction) a
summary of the relevant dimensions in physical units:  "The simulations
presented here are representative of a liquid crystal blue phase with unit
cell size in the range of 100--500~nm and particles with a radius of
around 50~nm." This new paragraph also serves the requirement for a brief
summary of the results as set out in the manuscript checklist.

RESPONSE (cont.): As a coarse-grained description of the mesophase, the
Landau-de Gennes  theory is appropriate as long as the size of the
colloidal particle is much larger than the size of the mesogen,
the latter being typically in the range of 1--10 nanometres. Our
simulations meet this criteria (particle size about 50 nm) and the
use of Landau-de Gennes is therefore justified.

@@

Is WR/K = 2.8 justified for nanoparticles used in the study?

RESPONSE: The choice of WR/K = 2.3 in the simulations (not 2.8)
is used to separate clearly a strong anchoring regime from a
weak anchoring regime (w = 0.23). While typical experimental
values for particles of this size may mean the weak regime is
more common, we do not see that this precludes interest in a
strong anchoring regime.

@@

Page 4:

Can the G elastic modulus be estimated for modeled structures?

RESPONSE: We note we did have, in the original manuscript, a
paragraph which discusses estimates of the elastic modulus G
based on analogy with experimentally observed systems. To the
existing paragraph we have appended:
"This figure is consistent with an estimate obtained by comparing
the mechanical properties of the network of defects stabilised by
colloidal particles with those of rubber [Ramos et al 2002] for
the relevant simulation parameters (see Supplementary Information)."
To the supplementary information we append: "For a Frank elastic
constant of $K = 70$~pN and unit cell sizes in the range
$\lambda =$100--500~nm, a corresponding shear modulus $G \simeq
K/\lambda^2 =$0.3--7~kPa." The relevant reference is added.

@@

Is also in case of the disordered structures observed a change in the
stability range of the colloidal BPs?

RESPONSE: Determining the stability range of the composite
phases was beyond the scope of this paper. This would have required 
an optimisation of the pitch length, which requires a large number 
of additional simulations for each individual parameter set.

In the discussion of colloidal particles in BP thin layers it would be good
to comment the study of
Ravnik et al. in Soft Matter 2011 devoted the ordered structures of such a
system.

RESPONSE: A citation for Ravnik et al (2011) has been added [current
reference 26].

@@

Page 6:

It would be good to comment the difference between structures in the bulk
and thin layer for particles with strong anchoring. Does this depend on the
visualization or is more behind?

RESPONSE: We have added the following at the end of the section
describing the confined geometry: "The degree of similarity between
the bulk and confined structures is somewhat masked by the local
change in particle density in the confined case. If one allows for
this, Figs.~1 and~2 show the individual structural motifs are actually
rather similar: templated lines for weak anchoring and clusters for
strong anchoring."

RESPONSE (cont.): One potential visualisation ambiguity is that the
displayed box sizes are different in each of the figures (cf. particle
size). An explicit statement has been added to each caption to make
this more clear to the reader. ADD CAPTIONS?

@@

RESPONSE: For the given parameters the field induced changes are only
irreversible when colloids with sufficiently strong 
anchoring conditions are present. The mesophase without colloids 
undergoes a reversible ordering transition as described in reference [10].
CHECK REFERENCE

Page 7

Reference 2 has a mistake.

RESPONSE: The correct punctuation in the page numbers has been
inserted in the reference for Wright and Mermin [current reference 9].

@@

Supplement

Segment 4.2:

The statement "Wall anchoring is either normal or planar with W=K = 1 in
simulation units" is unclear.

RESPONSE: This text has been replaced by a statement which is
transparent: "For both normal and planar anchoring at the walls,
the value of $W$ is the same as that used for the
strongly anchoring particles."

@@

References of the Supplement:
There are mistakes in references 1 and 2.

RESPONSE: Reference 1, Wright and Mermin, was correct in
the original supplement. Reference 2 has been updated to reflect
the 2nd edition of de Gennes and Prost, which now appears in the
main text [current reference 34].
CHECK REFERENCE

@@

Reviewer #2 (Remarks to the Author):

This paper, "Self-assembly of colloid-cholesteric composites: A route to
switchable optical materials" reports simulations of the formation of
particle networks in a cholesteric host and in
particular in the blue phase of the cholesteric host. It reports the
influence of various physical parameters and in particular the surface
anchoring and concentration of the colloidal
particles. The paper also reports how external fields can be employed to
change the morphology of these colloidal composites and how this may be
employed in practical optical devices.

The paper builds on a body of previous research, both theoretical and
experimental that has explored the effects of dispersing particles in a
liquid crystal host. The novelty of the paper is
to model the effect of particles in the blue phases of a cholesteric host
ahd to postulate how these colloids may be employed in specific
applications.

@@

I am not a theorteical physiscist and therefore will not comment on the
methodology but rather will take the perspective of an experimentalist and
how useful this paper is in understanding
these materials and more importantly how useful the paper is in suggesting
and designing experimental procedures and developing the actual materials.

The paper provides insight into the effectiveness of including particles
into the blue phase as a means of controlling and adjusting the structure
and stability of the materials. The paper
is clearly written and the figures, paricularly the included 3D videos,
provide clear perspective on the modeled phases of these materials. The
results are of interest and useful to
experimentalists working in the field.

The paper would be even more useful if it included references to actual 
materials, both the liquid crystal host and the added particles and perhaps
even suggested a model system that would be a good starting point to study
experimentally.

RESPONSE: In a new paragraph in the discussion section, we include six
new references specifically aimed at recent studies on experimental
nanoparticle liquid crystal composites. These are currently [34-39].
The paragraph also discusses the issue of a model system, and suggests
properties such a system may have to help match experiment and simulation.

@@

In a similar vein, it would also be useful to address the
practical issue of reproducibility, which has been a major problem 
with these materials. The theoretical results clearly indicate how important 
the formation conditions are to the final result.

What is the authors sense of how easy it will be to reproducibly fabricate a device
with a specific morphology and optical properties. This seems a likely
practical issue particularly with the rich variety of structures reported in
the simulations.

RESPONSE: Clearly the issue of experimental reproducibility is a difficult
one to be addressed by, of necessity idealised, simulation. However, one
point our simulations do show is that careful characterisation of not
only the particles and host fluid is required, but also of possible
confinement effects and associated anchoring conditions. This we also
address in our updated discussion.

The entire paragraph reads: ADD WHEN FINALISED

* ADDITIONAL CHANGES TO MEET FORMAT REQUIREMENTS
  cf Manuscript checklist

### 2014-03-03 papers/2012-sandwich/CholColloids.tex
Updated ms and response
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2323 40876441-3496-0410-a613-a2fca35b2ae2

\author{K. Stratford$^{*}$, O. Henrich$^{*}$, J.~S. Lintuvuori$^{*}$,\\
M. E. Cates, D. Marenduzzo$^\dagger$ \\ 
SUPA, School of Physics and Astronomy, The King's Buildings,\\
The University of Edinburgh, Edinburgh, EJ9 3JZ, UK\\
\small{$^{*}$ equally contributed to this work}\\
\small{$^\dagger$ Corresponding author: dmarendu@ph.ed.ac.uk}
}
\date{}

@@

A second compelling reason to study colloidal-BP composites is that, even without particles, BPs can show several competing metastable free energy minima,
corresponding to different topologies of the defect network~\cite{adriano,fukuda}, with a strong dependence on applied electric or magnetic fields~\cite{henrichfield}.
% 
Adding particles is likely to further enrich the free energy landscape, creating composites that might be promising candidates for bistable or multistable devices, in which energy is needed only to switch optical properties and not to maintain them. (This is the e-paper paradigm~\cite{epaper}, and can lead to huge energy savings.)
To explore such metastability, and switching strategies between states, we require multi-unit-cell, time-dependent simulations. These go beyond previous studies of colloidal-BP composites~\cite{miha} but follow comparable simulations of pure BPs~\cite{bp3,henrichfield,domaingrowth}, and isolated and dimeric colloidal particles in cholesterics~\cite{juho1,juho2}. Our methodology and simulation parameters are summarized in the Supplementary Information.

SHORT SUMMARY OF RESULTS AND CONCLUSIONS (PRESENT TENSE). To include a
statement about confined systems with reference to \cite{extrareference2}.
The simulations represent a liquid crystal
blue phase with unit cell size in the range of 100--500~nm \cite{mermin},
and particles with a radius of around 50~nm.

\bigskip
\noindent
\textbf{\large Results} [Currently about 1400 words]

@@

As colloidal-nematic composites~\cite{tiffany}, all the structures in
Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloidal-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.

@@

Fig.~2A-D shows the case of normal wall anchoring on varying $\phi$ and $w$. We quench from the isotropic to the ordered phase as was done in Fig.~1E-H, and again find a metastable, amorphous disclination network (see Supplementary Information). The resulting colloidal-cholesteric composites are somewhat similar to those seen in the bulk: for small $w$ the particles are templated by the network (Fig.~2A,B), whereas for large $w$ we observe isolated clusters (Fig.~2C) and percolated colloidal gels (Fig.~2D), for $\phi = 1\%$ and $4\%$ respectively. There are, however, significant effects of the confining walls.
First, the normal anchoring at the wall recruits particles there,  giving (for the chosen $h$) a density enhancement of the colloid particless at both walls 
(see side-views in Fig.~2A-D). Second, the clusters formed at large $w$ are themselves anisotropic with an oblate habit. These clusters
are similar to those reported experimentally for large colloid particles in a
cholesteric (but non-BP) host~\cite{niek}.

@@

\medskip
\noindent
\textbf{Switching in electric field.}
An interesting question, relevant for applications to devices, is whether 
these structures can be modified, or switched, with electric fields.
Fig.~3 addresses this question, starting from amorphous Blue Phase III,
this time at a higher chirality. Dispersing colloidal particles in this networks
results in the particle occupying the available nodes, where the order
parameter is low (Fig.~3A; Supplementary Movie~5). Applying a high enough
field 
along the $x$ direction leads to a switching to a new phase, where colloidal 
arrays fit within a network with distorted hexagonal cells (Fig.~3B 
and Supplementary Fig.~7; Supplementary Movie~6). 
Remarkably, upon field removal this honeycomb structure does not find its 
way back to the 
configuration before switching on the field, but gets stuck into a metastable 
structure (Supplementary Fig.~7), with residual anisotropy along the field
switching 
direction. Cycling the field along the $x$ and $y$ directions leads to
distinct metastable structures, which are retained after field removal
(Suplementary Fig.~8 and Fig.~9).

%FIELD SWITCHING PARA HERE
\if{The existence of several locally stable competing solids with 
very different symmetry and, arguably, physical properties, 
is of interest to technology, as it makes these materials ideal
candidate to build multistable devices, which can retain memory of
more than one metastable state in the absence of an applied field.
Multistability is indeed a must-have feature for new generation switchable 
electrooptic devices for use in energy-saving electronics-free
appliances, smart glass, and e-paper to cite just a few examples.
}\fi

\medskip
\noindent
\textbf{\large Discussion} [Currently about 260 words]

\noindent
The surprising wealth of colloidal-BP composites obtained in Figs.~1-3 is the complex consequence of a simple competition between two self-assembly principles. 
First, blue phases provide a three-dimensional template onto which colloidal particles are attracted so as to reduce the elastic stresses arising at the disclination cores~\cite{miha}. Second, colloidal intrusions in a liquid crystal raise the free energy locally; sharing this cost creates a generic tendency to aggregate into clusters~\cite{tiffany}. Which of these factors dominates depends on $w$, a dimensionless measure of the anchoring strength of the director field at the colloidal surface. For $w\ll 1$, the templating principle dominates. Colloidal crystals, gels or twisted rings can then arise. For $w \gg 1$, interparticle attractions defeat the templating tendency, and we predict disconnected aggregates, percolating gels, or helical colloidal ropes. In both cases, control is offered by the process route, colloidal concentration, and the anchoring conditions at sample walls. We have also shown that electric fields can be used to switch between metastable states, providing a possible route to future multistable device applications.
%This variety of metastable structures, with tunable properties that can combine the mechanical and optical features of colloid particles and liquid crystals~\cite{lavrentovich}, offers promise for the design of multistable liquid crystal devices, which are at the forefront of current technological developments in this field. 
We have not explored in this work switchability by flow \cite{flowswitch}, but this could again be inherited from the underlying BP dynamics \cite{adriano,permeation2}, in which case the same materials may also be relevant to the emerging technology of optofluidics~\cite{optofluidics}.

@@

INTRODUCTORY STATEMENT

\noindent
\textbf{Theromdynamics.}
The thermodynamics of the cholesteric liquid crystal can be described
by means of a  Landau-de Gennes free energy functional $\cal F$,
whose density is written as $f$:
\begin{eqnarray}
{\cal F}[{\bf Q}]&=&\int d^3{\bf r} f({\bf Q}({\bf r})).
\end{eqnarray}
This free energy density $f = f({\bf Q})$ may be expanded in powers of the
order parameter ${\bf Q}$ and its gradients; ${\bf Q}$ is a traceless 
and symmetric tensor which is denoted from now on in subscript
notation as $Q_{\alpha\beta}$.
The largest eigenvalue $q$ and corresponding eigenvector $n_\alpha$
of $Q_{\alpha\beta}$ describe the local strength and major orientation axis
of molecular order.
The theory based on the tensor $Q_{\alpha\beta}$, rather than a theory based
solely
on the director field $n_\alpha ({\bf r})$, allows treatment of disclinations
(defect lines) in whose cores $n_\alpha$ is undefined.

@@

\medskip
\noindent
\textbf{Protocol and parameter details for bulk BPI.}
The parameters for the free energy are chosen to be representative
of blue phase I: chirality $\kappa \sim 0.7$ and reduced temperature
$\tau = -0.25$.
The full free energy parameters are shown in Table~\ref{table:params}.
The order parameter tensor $Q_{\alpha\beta}$ for bulk blue phase I is
initialised from an approximation in high chirality limit
\cite{mermin,henrichfield}. Systems of 128$^3$ lattice sites are
used with a pitch length of $p = 32\sqrt{2}$, which accommodates 4$^3$
unit cells with fully periodic boundary conditions.
Simulations at different solid volume fractions (1\% and 4\%), and different 
surface anchoring strengths ($WR/K = 0.23$ and $WR/K = 2.3$) representing
``weak'' and ``strong'' anchoring are run for two million simulation
time steps.
The initial distribution of the particle positions is set at random
for the required solid volume fraction; the particles are initially
at rest.

\medskip
\noindent
\textbf{Parameter details for confined BPI.}
Here, a narrow sandwich of fluid is placed between flat walls in
perpendicular to the narrow coordinate direction, and with periodic
boundaries in the other two directions. The system size used in all
cases is 256$^2 \times$56 lattice sites. Each simulation is a ``quench''
in a similar manner to that used in the bulk: the order parameter is
initialised randomly. The free energy parameters (see Table~\ref{table:params})
are again appropriate for (equilibrium) blue phase I
(chirality $\kappa = 0.8$ and
reduced temperature $\tau = -0.25$). The cholesteric pitch is set
to be $p = 64$, providing a slightly better resolution than the bulk
simulations.

The surface anchoring for colloidal particles is as before: always normal,
but with
$WR/K = 0.23$ and $WR/K = 2.3$. The solid volume fractions are
1\% and 4\%.
\textcolor{red}{For both normal and planar anchoring at the walls,
values of $W$ and $K$ are used which are the same as for the
strongly anchoring particles.}
All simulations are run for two million simulation
time steps.

\medskip
\noindent
\textbf{Parameters for external electric field.}
For the simulations of BPIII with colloidal particles a system size of
$128^3$ is used with a cholesteric pitch of $p=32$ in lattice units. 
The simulations are
performed at chirality $\kappa=2.6$ and reduced temperature $\tau=-0.25$.  
An initial configuration of
randomly oriented and positioned double twist cylinders is used,
from which an amorphous BPIII network emerges \cite{bp3}. This structure
is equilibrated for $6\times10^{5}$ LB time steps until no significant
further evolution is observed.

The colloidal particles with weak
normal anchoring ($WR / K= 0.23$), are then inserted with randomly chosen positions,
and the composite system is equilibrated for another $1.2\times10^{6}$
time steps.
At the end of the equilibration phase the uniform electric field
with reduced field strength ${\cal E} = 0.8$ 
is switched on (oriented along the $z$-direction), and the simulation
run for a further $1.2\times10^{6}$ time steps.
This is found to be sufficiently long for a hexagonal structure to
emerge and saturate.
If the electric field is then switched off, and the system quickly relaxes
to a metastable state which shows a residual anisotropy in the
colloidal distribution. The total length of this final relaxation phase
is $1\times10^6$ LB time steps.

\medskip
\noindent
\textbf{Disclination rendering.}
In all cases visualisation of the defect lines is carried out via
an isosurface of the scalar order parameter $q$ determined from the
largest eigenvalue of the local order parameter tensor. A low value
of the scalar order parameter $q$ (typically in the range 0.12--0.14)
unambiguously identifies the disclinations.

\medskip
\noindent
\textbf{Computation of the structure factor.}
To provide structural information about the field-aligned 
states and the residual anisotropy after switch off a 
procedure similar to the one described in \cite{bp3} is
followed.
The structure factor $S(\mathbf{k})$ in the current approach is
defined via the Fourier transform of the particle density $F(\mathbf{k})$:

\begin{equation}
S({\bf k}) =  |F({\bf k})|^2, \mathrm{with}\
F({\bf k}) = \int d^3{\bf r} \rho({\bf r}) e^{i {\bf k. r}}.
\end{equation}
The colloidal density $\rho({\bf r})$ is a discretised density and taken to be
$\rho({\bf r})=1$ if a lattice site at ${\bf r}$ is part of a solid particle
and $\rho({\bf r})=0$ otherwise. This definition, which deviates from the 
standard definition of a structure factor and does not consider the particles 
as point-like objects, allows the same structural information
to be obtained in a simple way.

\medskip
\noindent
\textbf{Parameter mapping to physical units.}
To get from simulation to physical units, a calibration of scales of
length, energy and time in the simulations is required. For similar
mappings see, e.g.~\cite{denniston2}.

The length scale can be set by mapping the half pitch to a realistic blue
phase unit cell size, which is in the 100--500~nm range \cite{mermin}. 
For bulk simulations (Fig.~1 and Fig.~3 in the main text), a suitable choice
is one where one simulation unit (lattice site) corresponds to 10~nm. Therefore
the colloidal size in Figs.~1 and~3 corresponds to $\sim$ 50~nm.

To obtain an energy scale, it is possible to choose $A_0 \simeq 10^6$~Pa,
which is reasonable following Ref.~\cite{mermin} (this is also the choice in
Ref.~\cite{domaingrowth}). This choice leads to a simulation unit of
free energy (or stress) equal to $10^{8}$~Pa in Figs.~1 and~3.
From the energy and length scales one can map elastic constants to
physical units: for instance, the simulation in Fig.~1 corresponds to
a liquid crystal with splay, bend and twist (Frank) elastic constants
equal to 35 pN (or equivalently $K=70$~pN).

The timescale calibration may be obtained from (see e.g.~\cite{denniston})
\begin{equation}
\gamma_1=\frac{2q^2}{\Gamma},
\end{equation}
which relates the rotational viscosity $\gamma_1$ to the ordering strength
$q$ and the order parameter mobility $\Gamma$.
In the present simulations, $\Gamma = 0.5$ and the value of $\gamma$
for the simulation in Fig.~1 leads to $q=1/2$.   
For real liquid crystalline materials, $\gamma_1$ usually lies in range
$10^{-2}$--$1$~Pa~s~\cite{deGennes}; for definiteness say
$\gamma_1 = 1$~Pa~s (equivalently 10 poise). Given the previous mapping for
free energy (or stress) units, this leads to a simulation unit of time equal
to $10^{-8}$~s. The total simulated time in Figs.~1--3 is therefore in the
millisecond range.

To calibrate the electric field strength 
one can equate the value of the dimensionless parameter ${\cal E}$ in the 
simulations with that of a hypothetical experiment.
Given the previous value for $A_0$, and a dielectric anisotropy of 20
(or equivalently $\epsilon_a=20\epsilon_0$, with $\epsilon_0$ the
dielectric permittivity of vacuum), an electric field
of 100 V~$\mu$m$^{-1}$ is obtained. This corresponds to a value of
${\cal E}\sim 0.4$ (considering a value of $\gamma=3.0857$ as in
Fig.~3 of the main text).

Given these mappings, all quantities can be easily transformed from
simulation to physical units and vice versa. For example Figs.~1 and~2
use an isotropic viscosity $\eta \simeq$~0.01 and~0.1 in simulation units,
which translate into $0.01$--$0.1$~Pa~s respectively. This is sensible (if 
slightly low) for a molecular nematogen in the isotropic phase. 
The effective viscosity in ordered phases is higher, but this is ensured
in our model by the coupling to the order parameter.
Note that the density is set to unity in the simulations: this
corresponds to a fluid density which is about a thousand times larger
than in experiments. This makes no difference in practice as
the Reynolds number $= \rho V\Lambda/\eta$ (where $V$ is a typical
velocity, in our simulations around $10^{-5}$ in lattice units, 
and $\Lambda$ is a typical length scale, e.g. the size of a unit cell) 
remains small enough~\cite{codef}.

To summarise, the simulations represent BP-forming materials, with the
interpretation of the simulation units for length, time, and energy
density being close to 10~nm, 10~ns, and 100~MPa respectively.

@@

\bibitem{wiresmiha} M. Ravnik, M. Skarabot, S. Zumer, U. Tkalec, I. Poberaj,
D. Babic, N. Osterman, I. Musevic,
Entangled nematic colloidal dimers and wires, 
{\it Phys. Rev. Lett.} {\bf 99}, 247801 (2007).

\bibitem{zumer}
I. Musevic, M. Skarabot, U. Tkalec, M. Ravnik, S. Zumer,
Two-dimensional nematic colloidal crystals self-assembled by topological
defects,
{\it Science} {\bf 313}, 954--958 (2006).

\bibitem{tanaka} T. Araki, H. Tanaka,
Colloidal aggregation in a nematic liquid crystal: Topological arrest of
particles by a single-stroke disclination line,
{\it Phys. Rev. Lett.} {\bf 97}, 127801 (2006).

\bibitem{tiffany}
T.~A. Wood, J.~S. Lintuvuori, A.~B. Schofield, D. Marenduzzo, W.~C.~K. Poon,
A Self-Quenched Defect Glass in a Colloid-Nematic Liquid Crystal Composite,
{\it Science} {\bf 333}, 79--83 (2011).

\bibitem{stark} H. Stark,
Physics of colloidal dispersions in nematic liquid crystals,
{\it Phys. Rep.} {\bf 351}, 387--474 (2001).

>>>>

\author{K. Stratford$^{*}$, O. Henrich$^{*}$, J.~S. Lintuvuori$^{*}$,\\
M. E. Cates, D. Marenduzzo$^\dagger$ \\ 
SUPA, School of Physics and Astronomy, The King's Buildings,\\
The University of Edinburgh, Edinburgh, EH9 3JZ, UK\\
\small{$^{*}$ equally contributed to this work}\\
\small{$^\dagger$ Corresponding author: dmarendu@ph.ed.ac.uk}
}
\date{}

@@

A second compelling reason to study colloidal-BP composites is that, even without particles, BPs can show several competing metastable free energy minima,
corresponding to different topologies of the defect network~\cite{adriano,fukuda}, with a strong dependence on applied electric or magnetic fields~\cite{henrichfield}.
% 
Adding particles is likely to further enrich the free energy landscape, creating composites that might be promising candidates for bistable or multistable devices, in which energy is needed only to switch optical properties and not to maintain them. (This is the e-paper paradigm~\cite{epaper}, and can lead to huge energy savings.)
To explore such metastability, and switching strategies between states, we require multi-unit-cell, time-dependent simulations. These go beyond previous studies of colloidal-BP composites~\cite{miha} but follow comparable simulations of pure BPs~\cite{bp3,henrichfield,domaingrowth}, and isolated and dimeric colloidal particles in cholesterics~\cite{juho1,juho2}.

\textcolor{red}{
The simulations presented here are representative of a liquid crystal
blue phase with unit cell size in the range of 100--500~nm \cite{mermin},
and particles with a diameter of around 50~nm. The simulations
address both the bulk structure, and the structure which forms when
the colloidal dispersion is confined in a narrow sandwich of width
comparable to the unit cell size~\cite{extrareference2}. It is seen
that a wide variety of structure is possible, and may be influenced
by parameters including the solid volume fraction, and the details
of the anchoring at the colloid surface (and the at the surface of the
confining walls). Further, evidence is found for metstable switching of
this structure in an applied electric field. Details of the
computational approach are set out in the Methods section, while
simulation parameters are reported in the Supplementary Information.
}

\bigskip
\noindent
\textbf{\large Results}

@@

As colloidal-nematic composites~\cite{tiffany}, all the structures in
Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloidal-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.
\textcolor{red}{
This figure is consistent with an estimate obtained by comparing
the mechanical properties of the network of defects stabilised by
colloidal particles with those of rubber~\cite{ramos} for
the relevant simulation parameters (see Supplementary Information).}

@@

Fig.~2A-D shows the case of normal wall anchoring on varying $\phi$ and $w$. We quench from the isotropic to the ordered phase as was done in Fig.~1E-H, and again find a metastable, amorphous disclination network (see Supplementary Information). The resulting colloidal-cholesteric composites are somewhat similar to those seen in the bulk: for small $w$ the particles are templated by the network (Fig.~2A,B), whereas for large $w$ we observe isolated clusters (Fig.~2C) and percolated colloidal gels (Fig.~2D), for $\phi = 1\%$ and $4\%$ respectively. There are, however, significant effects of the confining walls.
First, the normal anchoring at the wall recruits particles there,  giving (for the chosen $h$) a density enhancement of the colloid particles at both walls 
(see side-views in Fig.~2A-D). Second, the clusters formed at large $w$ are themselves anisotropic with an oblate habit. These clusters
are similar to those reported experimentally for large colloid particles in a
cholesteric (but non-BP) host~\cite{niek}.

@@

\textcolor{red}{
The degree of similarity between
the bulk and confined structures is somewhat masked by the local
change in particle density in the confined case. If one allows for
this, Figs.~1 and~2 show the individual structural motifs are actually
rather similar: templated lines for weak anchoring and clusters for
strong anchoring.
}

\medskip
\noindent
\textbf{Switching in electric field.}
An interesting question, relevant for applications to devices, is whether 
these structures can be modified, or switched, with electric fields.
Fig.~3 addresses this question, starting from amorphous Blue Phase III,
this time at a higher chirality. Dispersing colloidal particles in this networks
results in the particle occupying the available nodes, where the order
parameter is low (Fig.~3A; Supplementary Movie~5). Applying a high enough
field 
along the $x$ direction leads to a switching to a new phase, where colloidal 
arrays fit within a network with distorted hexagonal cells (Fig.~3B 
and Supplementary Fig.~7; Supplementary Movie~6). 
Remarkably, upon field removal this honeycomb structure does not find its 
way back to the 
configuration before switching on the field, but gets stuck into a metastable 
structure (Supplementary Fig.~7), with residual anisotropy along the field
switching 
direction. Cycling the field along the $x$ and $y$ directions leads to
distinct metastable structures, which are retained after field removal
(Supplementary Fig.~8 and Fig.~9).

\medskip
\noindent
\textbf{\large Discussion}

\noindent
The surprising wealth of colloidal-BP composites obtained in Figs.~1-3 is
the complex consequence of a simple competition between two self-assembly
principles. 
First, blue phases provide a three-dimensional template onto which
colloidal particles are attracted so as to reduce the elastic stresses
arising at the disclination cores~\cite{miha}. Second, colloidal intrusions
in a liquid crystal raise the free energy locally; sharing this cost creates
a generic tendency to aggregate into clusters~\cite{tiffany}. Which of these
factors dominates depends on $w$, a dimensionless measure of the anchoring
strength of the director field at the colloidal surface. For $w\ll 1$, the
templating principle dominates. Colloidal crystals, gels or twisted rings
can then arise. For $w \gg 1$, interparticle attractions defeat the
templating tendency, and we predict disconnected aggregates, percolating
gels, or helical colloidal ropes. In both cases, control is offered by the
process route, colloidal concentration, and the anchoring conditions at
sample walls. We have also shown that electric fields can be used to
switch between metastable states, providing a possible route to future
multistable device applications.

\textcolor{red}{
How do these simulations relate to experiment? Several authors have
used nanoparticles in the context of stabilising BPs
\cite{yoshida2009,karatairi}. These
nanoparticles are typically a few nanometres in size, in which case
stabilisation is explained by the mechanism of defect removal.
Experiments suggest this mechanism is also
relevant for larger particles in the range of 40--70~nm 
\cite{dierking}, which is consistent with the current simulations.
However, the mechanism is observed to be less efficient for
particles above 100~nm, where particles may start to disrupt
longer-range liquid crystal order \cite{dierking}. While the field of
self-assembly with nanoparticles is relatively new \cite{draper},
nanoparticles have also been used in both nematic \cite{milette2012}
and chiral liquid crystals \cite{cordoyiannis} as host fluid templates.
The variation of structure seen
in our simulations suggest that some careful characterisation of parameters
such as surface anchoring of particles (which are often stabilised, or even
functionalised with surface ligands), together with those associated
with any confining surfaces or interfaces, is required to understand the
final structure and to be able to reproduce it with a given experimental
protocol. The identification of a model system which could allow
unambiguous comparison between experimental systems and simulation
would be extremely useful. Such a system might adopt particles of
dimeter in the range 50~nm or above, which allows a coarse-grained simulation
approach of the type used here to be adopted, which can then capture the
large-scale structure required to compare with experiment. In the same vein,
detailed surface chemistry is difficult to represent in coarse-grained
simulations, so heavily functionalised particles might be avoided.
}

We have not explored in this work switchability by flow \cite{flowswitch}, but this could again be inherited from the underlying BP dynamics \cite{adriano,permeation2}, in which case the same materials may also be relevant to the emerging technology of optofluidics~\cite{optofluidics}.

@@

Here, the simulation method is described. Note that
all quantities are expressed in simulation units. Details
of the simulation parameters, and their mapping to physical units,
may be found in the Supplementary Information.

\medskip
\noindent
\textbf{Thermodynamics.}
The thermodynamics of the cholesteric liquid crystal can be described
by means of a  Landau-de Gennes free energy functional $\cal F$,
whose density is written as $f$:
\begin{eqnarray}
{\cal F}[{\bf Q}]&=&\int d^3{\bf r} f({\bf Q}({\bf r})).
\end{eqnarray}
This free energy density $f = f({\bf Q})$ may be expanded in powers of the
order parameter ${\bf Q}$ and its gradients; ${\bf Q}$ is a traceless 
and symmetric tensor which is denoted from now on in subscript
notation as $Q_{\alpha\beta}$.
The largest eigenvalue $q$ and corresponding eigenvector $n_\alpha$
of $Q_{\alpha\beta}$ describe the local strength and major orientation axis
of molecular order.
The theory based on the tensor $Q_{\alpha\beta}$, rather than a theory based
solely
on the director field $n_\alpha ({\bf r})$, allows treatment of disclinations
(defect lines) in whose cores $n_\alpha$ is undefined.

@@

@@

\bibitem{wiresmiha}
Ravnik, M., et al.,
%M. Ravnik, M. Skarabot, S. Zumer, U. Tkalec, I. Poberaj,
%D. Babic, N. Osterman, I. Musevic,
Entangled nematic colloidal dimers and wires, 
{\it Phys. Rev. Lett.} {\bf 99}, 247801 (2007).

\bibitem{zumer}
%I. Musevic, M. Skarabot, U. Tkalec, M. Ravnik, S. Zumer,
Musevic, I., Skarabot, M., Tkalec, U., Ravnik, M., and Zumer, S.,
Two-dimensional nematic colloidal crystals self-assembled by topological
defects,
{\it Science} {\bf 313}, 954--958 (2006).

\bibitem{tanaka}
Araki, T., and Tanaka, H.,
Colloidal aggregation in a nematic liquid crystal: Topological arrest of
particles by a single-stroke disclination line,
{\it Phys. Rev. Lett.} {\bf 97}, 127801 (2006).

\bibitem{tiffany}
%T.~A. Wood, J.~S. Lintuvuori, A.~B. Schofield, D. Marenduzzo, W.~C.~K. Poon,
Wood, T.A., Lintuvuori, J.S., Schofield, A.B, Marenduzzo, D., and
Poon, W.C.K.,
A Self-Quenched Defect Glass in a Colloid-Nematic Liquid Crystal Composite,
{\it Science} {\bf 333}, 79--83 (2011).
